cardinalR: Generating interesting high-dimensional data structures

### 2025-10-05 paper-cardinalR.Rmd
Removed Cube projections

A cube structure (`r knitr::asis_output(if (knitr::is_html_output()) { "Figure \\@ref(fig:cube)"} else { "Figure \\@ref(fig:cube-proj)"})`) represents uniformly or systematically distributed points within a high-dimensional hypercube, providing a useful framework for assessing how well algorithms preserve uniformity, spacing, and boundary properties in high dimensions. We provide a set of functions to generate high-dimensional cube structures with flexible configurations, including regular grids, uniform random points, and cubes with missing regions or holes. These structures are valuable for testing the ability of algorithms to maintain uniform spacing or to detect gaps in the data. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:cube-tb-html)', '\\@ref(tab:cube-tb-pdf)'))` outlines these functions and their purposes.

@@

```{r}
gridcube_lang <- langevitour::langevitour(gridcube, levelColors = "black", enableControls = FALSE, width = "400px", height = "300px")
```

```{r gridcube-proj1}
scaled_data <- scale_data_manual(gridcube)

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.7, 
                                              axis_pos_y = -0.7, 
                                              threshold = 0.022))

gridcube_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.83, 0.8), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r gridcube-proj2}

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.8,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.85, 
                                              axis_pos_y = -0.85, 
                                              threshold = 0.05))

gridcube_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-1, 1), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r gridcube-proj3}

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.6,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.7, 
                                              axis_pos_y = -0.7, 
                                              threshold = 0.016))

gridcube_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.8, 0.8), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

```{r}
unifcube_lang <- langevitour::langevitour(unifcube, levelColors = "black", enableControls = FALSE, width = "400px", height = "300px")
```

```{r unifcube-proj1}
scaled_data <- scale_data_manual(unifcube)

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.75, 
                                              axis_pos_y = -0.75, 
                                              threshold = 0.022))

unifcube_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.9, 0.8), 
  title = "b1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r unifcube-proj2}

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.75, 
                                              axis_pos_y = -0.75, 
                                              threshold = 0.04))

unifcube_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.9, 0.8), 
  title = "b2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r unifcube-proj3}

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.65, 
                                              axis_pos_y = -0.65, 
                                              threshold = 0.016))

unifcube_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.8, 0.8), 
  title = "b3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

```{r cube, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `gridcube`, `unifcube`, and `cubehole` data in $4\\text{-}D$."}

cubefig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    gridcube_lang, unifcube_lang
  ),
  device = "xs"
)

class(cubefig) <- c(class(cubefig), "htmlwidget")

cubefig
```

```{r cube-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridcube` (a1-a3), `unifcube` (b1-b3), and `cubehole` (c1-c3) data.", fig.width=12, fig.height=8}

gridcube_proj1 + gridcube_proj2 + gridcube_proj3 +
unifcube_proj1 + unifcube_proj2 + unifcube_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

>>>>

A cube structure represents uniformly or systematically distributed points within a high-dimensional hypercube, providing a useful framework for assessing how well algorithms preserve uniformity, spacing, and boundary properties in high dimensions. We provide a set of functions to generate high-dimensional cube structures with flexible configurations, including regular grids, uniform random points, and cubes with missing regions or holes. These structures are valuable for testing the ability of algorithms to maintain uniform spacing or to detect gaps in the data. Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:cube-tb-html)', '\\@ref(tab:cube-tb-pdf)'))` outlines these functions and their purposes.

@@

@@

@@

### 2025-10-05 paper-cardinalR.tex
Removed Cube projections

A cube structure (Figure \ref{fig:cube-proj}) represents uniformly or systematically distributed points within a high-dimensional hypercube, providing a useful framework for assessing how well algorithms preserve uniformity, spacing, and boundary properties in high dimensions. We provide a set of functions to generate high-dimensional cube structures with flexible configurations, including regular grids, uniform random points, and cubes with missing regions or holes. These structures are valuable for testing the ability of algorithms to maintain uniform spacing or to detect gaps in the data. Table \ref{tab:cube-tb-pdf} outlines these functions and their purposes.

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/cube-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gridcube` (a1-a3), `unifcube` (b1-b3), and `cubehole` (c1-c3) data.}\label{fig:cube-proj}
\end{figure}

>>>>

A cube structure represents uniformly or systematically distributed points within a high-dimensional hypercube, providing a useful framework for assessing how well algorithms preserve uniformity, spacing, and boundary properties in high dimensions. We provide a set of functions to generate high-dimensional cube structures with flexible configurations, including regular grids, uniform random points, and cubes with missing regions or holes. These structures are valuable for testing the ability of algorithms to maintain uniform spacing or to detect gaps in the data. Table \ref{tab:cube-tb-pdf} outlines these functions and their purposes.

@@
